---
title: Pizza Dough
author: ''
date: '2024-08-17'
slug: pizza-dought
categories:
  - Recipes
tags:
  - Dough
  - Pizza
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, warning = F, message = F)
library(tidyverse)
library(kableExtra)
```

by B

# Ingredients

```{r}
ingredients <- 
  tribble(
    ~Ingredient, ~Amount,
    'Warm Water', '325 - 340 g',
    'Sugar', "1 tsp",
    'Yeast', '2 1/4 tsp OR 1 package',
    'All Purpose Flour OR Bread Flour', '500 g',
    'Olive Oil', '1 Tbsp + for coating',
    'Salt', '1 tsp'
  )

knitr::kable(ingredients, align = 'lr') |> 
  kable_styling(full_width = T) |>
  add_header_above(c("Yields 1 batch" = 2))

```


# Preparation 

1. Combine the water, sugar, and yeast in a small bowl.

2. Place the flour into a bowl, and add the salt along with the olive oil.

3. Add the yeast mixture and mix/knead with until you have a stretchy dough. 
    - NOTE: If using a stand mixer, leave it on for ~5 minutes with the dough hook attachment.

4. Cover the dough ball with a light layer of olive oil and place into a bowl. 

5. Cover the dough with plastic wrap.

6. Let rise in the bowl until doubled. 
