---
title: 'SQL: Zero to Advanced pt. 1'
author: "Zach Hedeen"
date: "2024-08-09"
slug: "sql-zero-to-advanced-pt-1"
categories: Learning
tags:
- Coding
- SQL
- Notes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, message = F, warning = F)
library(tidyverse)
library(kableExtra)
```

*materials by Bosscoder Academy, found on LinkedIn*

# Format

&emsp; The materials are sorted into 24 "days" of learning, each with a central theme. My goal is to break them into 3 posts, 8 "days" each, with a distillation of the already brief material in each section as a review of SQL. 

# 1. Introduction to SQL and Relational Databases 

## 1.1 Content

**SELECT** -

**INSERT** -

**UPDATE** -

**DELETE** -

## 1.2 Practice Questions
```{r}
practice_1 <- tribble(
  ~Question, ~Answer,
  'Write a SQL query to insert a new record into the "employees" table', 'Answer',
  'Write a SQL query to update the "quantity" column of the "products" table to 10 where the "product_id" is 5.', 'answer',
  'Write a SQL query to delete all records from the "orders" able where the "status" is "cancelled"', "ans"
)

knitr::kable(practice_1, align = "l") |>
  kable_styling(full_width = T) |>
  column_spec(1, width = '50%') |>
  row_spec(0, align = 'c')

```


# 2. Introduction to SQL and Relational Databases 

## 2.1 Content

**SELECT** - Determines which columns will be displayed. Use * to select all available columns

**INSERT** -

**UPDATE** -

**DELETE** -

## 2.2 Practice Questions
```{r}
practice_2 <- tribble(
  ~Question, ~Answer,
  'Write a SQL query to insert a new record into the "employees" table', 'Answer \n test of concept test again',
  'Write a SQL query to update the "quantity" column of the "products" table to 10 where the "product_id" is 5.', 'answer',
  'Write a SQL query to delete all records from the "orders" able where the "status" is "cancelled"', "ans"
)

knitr::kable(practice_1, align = "l") |>
  kable_styling(full_width = T) |>
  column_spec(1, width = '50%') |>
  row_spec(0, align = 'c')

```



