---
title: Bao Dough
author: B
date: '2024-08-13'
slug: bao-dough
categories:
  - Bao
tags:
  - Bread
  - Dough
  - Bao
  - Revenge
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, warning = F, message = F)
library(tidyverse)
library(kableExtra)
```

by B

# Ingredients

```{r}
ingredients <- 
  tribble(
    ~Ingredient, ~Amount,
    'Water ~Body Temperature', '236 g',
    'Yeast', "6 g",
    'Flour', '381 g',
    'Cornstarch', '78 g',
    'Sugar', '70 g',
    'Salt', '12 g',
    'Pork fat OR Butter', '2 Tbsp'
  )

knitr::kable(ingredients, align = 'lr') |> 
  kable_styling(full_width = T) |>
  add_header_above(c("Yields 1 batch" = 2))

```


# Preparation 

1. Add yeast to the water - let stand until foamy.

2. Mix flour, cornstarch, sugar, and salt in the stand mixer bowl.

3. Add the water mixture and mix until a cohesive ball forms. 

4. Once the ball is formed, add the pork fat a little bit at a time until it is all added. 

5. Let rise for **1.5 hours** (or until doubled).

6. *Don't forget to oil the bowl while the dough is rising.*

7. Fill with the filling of your choice and steam for 13 minutes so that they are fluffy. 