---
title: Chinese BBQ Pork
author: B
date: '2024-08-13'
slug: chinese-bbq-pork
categories:
  - Meat
tags:
  - Chinese
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, warning = F, message = F)
library(tidyverse)
library(kableExtra)
```

by B

# Ingredients

```{r}
ingredients <- 
  tribble(
    ~Ingredient, ~Amount,
    'Pork shoulder, cut into slabs', '1-3 lbs',
    'Brown Sugar', '3 Tbsp',
    'Honey', '3 Tbsp',
    'Chinese 5-Spice', '1.5 tsp',
    'Shaoxing Rice Wine', '2 Tbsp',
    'Soy Sauce', '1 Tbsp',
    'Hoisin Sauce', '2 Tbsp (+1 if no Bean Curd)',
    'Red or Black Bean Curd', '1 Tbsp',
    'Sesame Oil', '1 Tbsp',
    'Salt', '2 Tbsp'
  )

knitr::kable(ingredients, align = 'lr') |> 
  kable_styling(full_width = T) |>
  add_header_above(c("Yields ~1-3 lbs" = 2))

```


## Preparation 

1. Mix brown sugar, 5-spice, shaoxing rice wine, soy sauce, hoisin sauce, bean curd, sesame oil, and sea salt together in a bowl. 

2. Reserve 3 Tbsp marinade in a separate bowl, and mix in the honey to make the glaze.

3. Place the pork shoulder in with the marinade and marinade over night. 

--- 

4. Roast pork at 425 degrees F, flipping half way through.
  - Roast to an internal temperature of 158 degrees F.
  - Baste with glaze during the last 10 minutes of cooking time. 

# For a Pork Bun Filling

```{r}
ingredients <- 
  tribble(
    ~Ingredient, ~Amount,
    'BBQ Pork', '320 g',
    'Oil', '2 Tbsp',
    'Small Onion', '1',
    'Hoisin Sauce', '2 Tbsp',
    'Soy Sauce', '1.5 Tbsp',
    'Sugar', '2 tsp',
    'Water', '1/2 Cup',
    'Flour', '2 Tbsp'
  )

knitr::kable(ingredients, align = 'lr') |> 
  kable_styling(full_width = T)
```

## Preparation

1. Add flour to water. 

2. Head oil, cook onion until translucent.

3. Add hoisin, soy sauce, sugar, and water slurry. 

4. Cook until thick.

5. Add BBQ Pork.